Humann2 bar plot for gene family

### 2019-10-20 scripts/12_lefse_genefam_term_ggplot.Rmd
haha able to retrieve the actual term of KO

---
title: "Humann2 bar plot for gene family"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

######################################## Bash ########################################

```{bash}
# needs to download the utility mapping db first
humann2_databases --download utility_mapping full /Users/daia1/melodyP/data/humann2_res
```

```{bash}
# regroup to KEGG Orthogroups (KOs)
humann2_regroup_table \
            --input ../data/humann2_res/humann2_genefamilies.tsv  \
            --groups uniref90_ko  \
            --output ../data/humann2_res/humann2_genefamilies_KO_regroup.tsv
```

```{bash}
# renorm to relab
humann2_renorm_table  --input ../data/humann2_res/humann2_genefamilies_KO_regroup.tsv -u relab --output ../data/humann2_res/humann2_genefamilies_KO_regroup_relab.tsv
```

```{bash}
# split into unstratified and ..
humann2_split_stratified_table --input ../data/humann2_res/humann2_genefamilies_KO_regroup_relab.tsv  --output ../data/humann2_res/genefamily_split_KO
```

######################################## R ########################################

## What features(gene orthologs) do you wanna see? Do lefse first.

@@

# join all of the tables feature together
feature <- fns %>% 
  set_names(fns_name) %>% 
  # when meeting parsing failures, you need to specify all column types.
  map(~ read_tsv(., col_names = c('genefam','xx','direction','score','pval'),  col_types = 'ccccc') %>% 
        filter(!is.na(score))) %>% 
  bind_rows(.id = 'group') %>% 
  mutate(group = str_replace(group, 'genefam_abundace_pheno__','')) %>% 
  mutate(group = str_replace(group, '.res$','')) %>% 
  select(-xx, -pval)

@@

feature %>% 
  write_csv('../data/lefse_genefam/with_unmapped_sig_feature.csv')

@@

>>>>

---
title: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(KEGGREST)
```

## Load the lefse results

@@

# join all of the tables feature together
feature <- fns %>% 
  set_names(fns_name) %>% 
  # when meeting parsing failures, you need to specify all column types.
  map(~ read_tsv(., col_names = c('genefam','xx','direction','score','pval'),  col_types = 'ccccc') %>% 
        filter(!is.na(score))) %>% 
  bind_rows(.id = 'group') %>% 
  mutate(group = str_replace(group, 'genefam_abundace_pheno__','')) %>% 
  mutate(group = str_replace(group, '.res$','')) %>% 
  select(-xx, -pval) %>% 
  mutate(KOID = str_replace(genefam, '\\.g.+$',''))

@@

# feature %>% 
#   write_csv('../data/lefse_genefam/with_unmapped_sig_feature.csv')

@@

## Use KEGGREST pkg to get the actual term

### work on the Toxicity first

```{r}
tox_df <-  feature %>% 
  filter(group == 'Toxicity') %>% 
  split(cut_width(1:nrow(.), 10, boundary=0)) %>% 
  map(~ pull(.data = ., KOID) %>% 
        map(~ list(KO_name = keggGet(.)[[1]]$NAME,
             KO_def = keggGet(.)[[1]]$DEFINITION)) %>% 
        bind_rows()) %>% 
  bind_rows()
